\documentclass[a4paper,oneside,11pt]{article}

\usepackage[pdftex]{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{url}
\usepackage{multibib}
\usepackage[ManyBibs]{currvita}
\usepackage{charter} % charter, utopia, newcent, palatino, univers
\usepackage{eurosym}

% No date or location
\cvplace{}
\date{}



% Tune options.
\AtBeginDocument{
  % The heading font of the CV
  \renewcommand{\cvheadingfont}{\huge\bfseries} 
  % The heading font of a cvlist
  \renewcommand*{\cvlistheadingfont}{\large\bfseries}
  % The labels font
  \renewcommand*{\cvlabelfont}{\it}
  % The label skip
  \setlength{\cvlabelskip}{2ex}
  % The label/text separation
  \setlength{\cvlabelsep}{1em}
  % The width of the labels column
  % \settowidth{\cvlabelwidth}{\cvlabelfont bleh}
  \setlength{\cvlabelwidth}{4.0cm}
  % Name of the bibliography
  \renewcommand*{\bibname}{List of papers}
}



\begin{document}

\begin{cv}{Curriculum Vitae}
  \begin{cvlist}{Personal Information}
    \item[Name] Alastair James Arthur Price
    \item[Born] December 2nd, 1990
    \item[Email] alastairjprice@gmail.com
    \item[Email] alastairj.price@utoronto.ca
    \item[Telephone] +1 (416) 666-3345
  \end{cvlist}

\setlength{\cvlabelwidth}{2.3cm}   \begin{cvlist}{Academic Background}
    \item[PDF]  Postdoctoral Research Fellow under the supervision of Professor O. Anatole von Lilienfeld at University of Toronto/Acceleration Consortium. July 2025 - Current.
    \item[PDF]  Postdoctoral Research Fellow under the supervision of Professor O. Anatole von Lilienfeld and Professor Alán Aspuru-Guzik at University of Toronto/Acceleration Consortium. June 2023 - July 2025.
    \item[Ph.D.] Dalhousie University
    under the supervision of Professor Erin R. Johnson.
    Dissertation titled, ``New implementation of the exchange-hole dipole moment (XDM) dispersion method for large-scale materials simulations.'' January 2019 -  April 2023
    \item[B.Sc Hons 1st] Dalhousie University, under the supervision of Professor Erin R. Johnson. Dissertation
    titled ``Dispersion-corrected density-functional theory applied to enantiopure amino acids on model quartz surfaces.'' %September 2017 - May 2018
   % \item[B.Sc] B.Sc. in Chemistry from Dalhousie University 
    September 2016 - May 2019
    %\item[B.Sc] B.Sc in Chemistry from University of Toronto September 2008 - May 2013 (completed at Dalhousie University)
  \end{cvlist}

\setlength{\cvlabelwidth}{0.5cm}  \begin{cvlist}{Research Grants}
\item[2.] Data Factory for ML design of complex materials: applications in catalysis, quantum devices, functional materials. National Research Foundation of Singapore: National University of Singapore -- University of Toronto Grant. Lead PIs Sir Konstantin Novoselov FRS, and Alán Aspuru-Guzik, PIs Antonio Helio Castro Neto, Barbaros Ozyilmaz, Daria Andreeva, Li Qianxiao, Maciej Koperski, Teck Leong Tan, Jason Hattrick-Simpers, Aimy Bazylak, O. Anatole von Lilienfeld, Stephen G. Dale, Kedar Hippalgaonkar, Mohamad Moosavi, Collaborator {\emph{\bf{Alastair J. A. Price}}}, Aleksandr Rodin, Andrey Ustyuzhanin, Giovanni Vignale, Yang Bai, Ali Shayesteh, Brandon Sutherland, Chris Sutton, Simon See, Yang Juntao, Ong Wen Jie, Min Lin, Tianbo Li, Mercy Xu, Ge Qi. \$10,000,000, 2026 ({\bf Awarded}). 
\item[1.] AI for modeling defects and functional intelligent materials. National University of Singapore -- University of Toronto Seed Grant. PI - Professor O.\ Anatole von Lilienfeld, Co-PI Dr.\ Alastair J.\ A.\ Price, PI (NUS) - Dr.\ Stephen G. Dale, \$60,000, December 2024 - July 2026 ({\bf Awarded}).
\end{cvlist}

  \setlength{\cvlabelwidth}{0.5cm}\begin{cvlist}{Publications}

\item[] 573 total citations, $h$-index of 14, $i10$-index of 16 (Google Scholar,  January 2026)
         \item[18.] Stephen G Dale, Nikita Kazeev, \textbf{Alastair J. A. Price}, Victor Posligua, Stephan Roche, O Anatole von Lilienfeld, Konstantin S Novoselov, et al. AI4X Roadmap: Artificial Intelligence for the advancement of scientific pursuit and its future directions. arXiv preprint arXiv:2511.20976, 2025. https://doi.org/10.48550/arXiv.2511.20976 
          \item[17.] Abbott, J. W., Mera Acosta, C., Akkoush, A., Ambrosetti, A., Atalla, V., et al. (including {\bf{A. J. A. Price}}). Roadmap on Advancements of the FHI-aims Software Package. arXiv preprint arXiv:2505.00125, 2025.
https://arxiv.org/abs/2505.00125
          \item[16.] Danish Khan, \textbf{Alastair J. A. Price}, Maximilian L. Ach, O. Anatole von Lilienfeld. Adaptive hybrid density functionals. {\it Sci. Adv.}, \textbf{2025}, 11(5), eadt7769.
          \item[15.] Igor Poltavsky, Mirela Puleva, Anton Charkin-Gorbulin, Gregory Cordeiro Fonseca, Ilyes Batatia, Nicholas J. Browning, Stefan Chmiela, Mengnan Cui, J. Thorben Frank, Stefan Heinen, Bing Huang, Silvan Käser, Adil Kabylda, Danish Khan, Carolin Müller, {\bf Alastair J. A. Price}, Kai Riedmiller, Kai Töpfer, Tsz Wai Ko, Markus Meuwly, Matthias Rupp, Gabor Csanyi, O. Anatole von Lilienfeld, Johannes T. Margraf, Klaus-Robert Müller, Alexandre Tkatchenko. Crash Testing Machine Learning Force Fields for Molecules, Materials, and Interfaces: Molecular Dynamics in the TEA Challenge 2023. {\it Chem. Sci.}, \textbf{2025}, 16, 3738-3754.
          \item[14.] Igor Poltavsky, Mirela Puleva, Anton Charkin-Gorbulin, Gregory Cordeiro Fonseca, Ilyes Batatia, Nicholas J. Browning, Stefan Chmiela, Mengnan Cui, J. Thorben Frank, Stefan Heinen, Bing Huang, Silvan Käser, Adil Kabylda, Danish Khan, Carolin Müller, {\bf Alastair J. A. Price}, Kai Riedmiller, Kai Töpfer, Tsz Wai Ko, Markus Meuwly, Matthias Rupp, Gabor Csanyi, O. Anatole von Lilienfeld, Johannes T. Margraf, Klaus-Robert Müller, Alexandre Tkatchenko. Crash Testing Machine Learning Force Fields for Molecules, Materials, and Interfaces: Model Analysis in the TEA Challenge 2023. {\it Chem. Sci.}, \textbf{2025}, 16, 3720-3737.
          \item[13.] Lily M. Hunnisett, Nicholas Francia, Jonas Nyman, Nathan S. Abraham, Srinivasulu Aitipamula, Tamador Alkhidir, Mubarak Almehairbi, Andrea Anelli, Dylan M. Anstine, {\it et al.,} {\bf Alastair J. A. Price}, Louise S. Price, Sarah L. Price, Michael R. Probert, Angeles Pulido, and Alexandre Tkatchenko. The seventh blind test of crystal structure prediction: structure ranking methods. {\it Acta Crystallogr., Sect. B: Struct. Sci.} {\bf 2024}, 80(6), 548-574.
          \item[12.] Lily M. Hunnisett, Jonas Nyman, Nicholas Francia, Nathan S. Abraham, Claire S. Adjiman, Srinivasulu Aitipamula, Tamador Alkhidir, Mubarak Almehairbi, Andrea Anelli, Dylan M. Anstine, {\it et al.,} {\bf Alastair J. A. Price}, Louise S. Price, Sarah L. Price, Michael R. Probert, Angeles Pulido, and Alexandre Tkatchenko. The seventh blind test of crystal structure prediction: structure generation methods. {\it Acta Crystallogr., Sect. B: Struct. Sci.} {\bf 2024}, 80(6), 517-547.
          \item[11.]  R. Alex Mayo, {\bf Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. Assessment of the exchange-hole dipole moment dispersion correction for the energy ranking stage of the seventh crystal structure prediction blind test. {\it Acta Crystallogr. B}, {\bf 2024}, 80(6), 595-605.
          \item[10.] Stefan Heinen, Danish Khan, Guido Falk von Rudorff, Konstantin Karandashev, Daniel Jose Arismendi Arrieta, \textbf{Alastair J. A. Price}, Surajit Nandi, Arghya Bhowmik, Kersti Hermansson, O Anatole von Lilienfeld. Reducing Training Data Needs with Minimal Multilevel Machine Learning (M3L). {\it Mach. Learn.: Sci. Technol.} {\bf2024}, 5(2),025058.
          \item[9.] Cameron J. Nickerson, Kyle R. Bryenton, {\bf Alastair J. A. Price}, Erin R. Johnson. Comparison of Density-Functional Theory Dispersion Corrections for the DES15K Database. {\it J. Phys. Chem. A} {\bf 2023} 127(41), 8712-8722.
          \item[8.] {\bf Alastair J. A. Price}, R. Alex Mayo, Alberto Otero de la Roza, Erin R. Johnson. Accurate and efficient polymorph energy ranking with XDM-corrected hybrid DFT. {\it CrystEngComm} {\bf 2023}, 25(6), 953-960.
          \item[7.] {\bf Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM-corrected hybrid DFT with numerical atomic orbitals predicts molecular crystal energetics with unprecedented accuracy. {\it Chem. Sci.} {\bf 2023}, 14, 1252-1262.
          \item[6.] Miriam DeJong, {\bf Alastair J. A. Price}, Erik Mårsell, Tom Gary, Giang Nguyen, Erin R. Johnson, Sarah Burke. Small molecule binding to surface-supported single-site transition-metal reaction centres. {\it Nat. Comm.}  {\bf 2022}, 13(1), 1-10.
          \item[5.] Joseph A. Weatherby, Adrian F. Rumson, {\bf Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. A density-functional benchmark of vibrational free-energy corrections for molecular crystal polymorphism. {\it J. Chem. Phys.} {\bf 2022}, 156(11), 114108.
          \item[4.] {\bf Alastair J. A. Price}, Kyle R. Bryenton, Erin R. Johnson. Requirements for an accurate dispersion-corrected density functional. {\it J. Chem. Phys.} {\bf 2021}, 154(23), 230902. ({\bf top 10\% of all tracked research by Altmetric})
          \item[3.] {\bf Alastair J. A. Price}, Erin R. Johnson. Theoretical investigation of amino-acid adsorption on hydroxylated quartz surfaces: dispersion can determine enantioselectivity. {\it Phys. Chem. Chem. Phys.} {\bf 2020}, 22(29), 16571-16578. ({\bf 2020 PCCP Hot Article})
          \item[2.] Jeffery J. McDowell, Isabel Schick, {\bf Alastair J. A. Price}, Daniel Faulkner, Geoffrey Ozin. Pure blue emitting poly (3, 6-dimethoxy-9, 9-dialkylsilafluorenes) prepared via nickel-catalyzed cross-coupling of diarylmagnesate monomers {\it Macromolecules} {\bf 2013}, 46(17), 6794 - 6805.
          \item[1.] Daniel O. Faulkner*, Jeffrey J. McDowell*, {\bf Alastair J. A. Price*}, Doug D. Perovic, Nazir P. Kherani, Geoffrey A. Ozin. Measurement of absolute photoluminescence quantum yields using integrating spheres–Which way to go?. {\it Laser Photonics Rev.} {\bf 2012}, 6(6), 802-806. ({\bf * Joint First Author})
  \end{cvlist}

\setlength{\cvlabelwidth}{0.5cm}  \begin{cvlist}{Invited Talks}
\item[10.] \textbf{Alastair J. A. Price}. Toward Trustworthy Hybrid DFT in Autonomous Materials Research: Best Practices and Pitfalls. Seoul National University Workshop. Seoul, South Korea, 2025.
\item[9.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Density Functional Methods for Materials Chemistry. Accelerate Conference. Toronto, Canada. 2025.
\item[8.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Damping for Dispersion Corrected Density Functional Theory. The Institute for Functional Intelligent Materials (I-FIM). National University of Singapore, Singapore 2025 ({\bf Invited seminar}). 
\item[7.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Implementation of Machine Learned Adaptive Density Functional Theory within FHI-aims. Fritz-Haber-Institut der Max Planck, Berlin, Germany. 2025 ({\bf Invited seminar}).
\item[6.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Implementation of Machine Learned Adaptive Density Functional Theory within FHI-aims. Department of Chemistry University of Oviedo, Oviedo, Spain. 2025 ({\bf Invited seminar}).
\item[5.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive System-Specific Dispersion Corrections for Near-Perfect van der Waals Interactions in Density Functional Theory. Institute for Functional Intelligent Materials (I-FIM), National University of Singapore, Singapore, 2025 ({\bf Invited seminar}). 
\item[4.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Density Functional Theory. Theoretical Chemistry Seminars series, Department of Chemistry, University of Cambridge. Cambridge, United Kingdom. 2024 ({\bf Invited seminar}).
\item[3.] \textbf{Alastair J. A. Price}, Erin R. Johnson. The XDM dispersion method for local orbitals: Implementation and applications within the FHI-aims package. Physical, Theoretical and Computational Chemistry Virtual Seminar. 2023 ({\bf Invited seminar}).
\item[2.] \textbf{Alastair J. A. Price}, Erin R. Johnson. The XDM dispersion method for local orbitals: Implementation and applications within the FHI-aims package. National Research Council and University of Ottawa. Ottawa, Canada. 2022 ({\bf Invited seminar}).
\item[1.] \textbf{Alastair J. A. Price}, Perspective on how to best select your Density Functional Approximation. Grey Group, Department of Chemistry, University of Cambridge. Cambridge, United Kingdom. 2022 ({\bf Invited seminar}).
\end{cvlist}

\setlength{\cvlabelwidth}{0.5cm}  \begin{cvlist}{Conference Oral Presentations}

     \item[8.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Density Functional Theory. AI4X, National University of Singapore, Singapore, 2025 ({\bf Contributed seminar}).
     \item[7.] \textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Density Functional Theory. CSTCC, Dalhousie University, Halifax, Nova Scotia, Canada, 2024.
      \item[6.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM dispersion with local orbitals: Implementation in the FHI-aims package. Symposium on Chemical Physics. Waterloo, Canada. 2022.
      \item[5.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM dispersion with local orbitals: Implementation in the FHI-aims package. American Chemical Society Fall Conference. Chicago, USA. 2022.
      \item[4.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM-corrected hybrid functionals for polymorph energy ranking. American Chemical Society Fall Conference. Chicago, USA. 2022.
      \item[3.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM-corrected hybrid DFT with numerical local orbitals calculates molecular crystal energetics with unprecedented accuracy. 12th Triennial Congress of the World Association of Theoretical and Computational Chemists (WATOC). Vancouver, Canada. 2022 ({\bf Invited communication}).
      \item[2.] \textbf{Alastair J. A. Price}, Erin R. Johnson. The Effect of Base Density Functional on the Performance of the Many-Body Dispersion Correction. Virtual Symposium on Theoretical and Computational Chemistry in Canada (VSTC3). 2021 Virtual.
      \item[1.] \textbf{Alastair J. A. Price}, Erin R. Johnson. Dispersion-corrected Density-functional Theory Applied to Amino-acid Adsorption on Model Quartz Surfaces. 102nd Canadian Chemistry Conference and Exhibition. Quebec City, Canada. 2019.
  \end{cvlist}

\setlength{\cvlabelwidth}{0.5cm}  \begin{cvlist}{Conference Poster Presentations}
      \item[9.]\textbf{Alastair J. A. Price}, O. Anatole von Lilienfeld. Adaptive Damping for Dispersion Corrected Density Functional Theory. Artificial Intelligence for Advanced Materials. San Sebastian-Donostia, Spain, 2025.   \item[8.] Danish Khan, \textbf{Alastair J. A. Price}, Maximilian L. Ach, O. Anatole von Lilienfeld. Adaptive hybrid density functionals. Chemical Compound Space Conference. Heidelberg, Germany. 2024.
      \item[7.] Stefan Heinen, Danish Khan, Guido Falk von Rudorff, Konstantin Karandashev, Daniel Jose Arismendi Arrieta, {\bf Alastair J. A. Price}, Surajit Nandi, Arghya Bhowmik, Kersti Hermansson, O Anatole von Lilienfeld. Reducing Training Data Needs with Minimal Multilevel Machine Learning (M3L). Accelerate Conference. Toronto, Canada. 2023.
      \item[6.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM dispersion with local orbitals: Implementation in the FHI-aims package. 29th Canadian Symposium on Theoretical and Computational Chemistry (CSTCC). Kelowna, Canada. 2022 ({\bf Awarded best graduate student poster}).
      \item[5.] \textbf{Alastair J. A. Price}, Alberto Otero de la Roza, Erin R. Johnson. XDM dispersion with local orbitals: Implementation in the FHI-aims package. 12th Triennial Congress of the World Association of Theoretical and Computational Chemists (WATOC). Vancouver, Canada. 2022.
      \item[4.] \textbf{Alastair J. A. Price}, Erin R. Johnson. Dispersion-corrected Density-functional Theory Applied to Amino Acid Adsorption on Model Quartz Surfaces. 28th Canadian Symposium on Theoretical and Computational Chemistry (CSTCC). Windsor, Canada. 2018.
      \item[3.] \textbf{Alastair J. A. Price}, Erin R. Johnson. Dispersion-Corrected Density-Functional Theory Applied to Amino-Acid Adsorption on Model Quartz Surfaces. ChemCon 2018 - Science Atlantic. Halifax, Canada. 2018.
      \item[2.] \textbf{Alastair J. A. Price}, Erin R. Johnson. Dispersion-corrected DFT Study of Enantiospecific Adsorption of Amino Acids on Hydroxylated Quartz Surfaces. 11th Triennial Congress of the World Association of Theoretical and Computational Chemists (WATOC). Munich, Germany. 2017.      
      \item[1.] \textbf{Alastair J. A. Price}, Erin R. Johnson. Dispersion-Corrected DFT Study of Enantiospecific Adsorption of Amino Acids on Hydroxylated Quartz Surfaces. Atlantic Theoretical Chemistry Symposium. Halifax, Canada. 2017.
  \end{cvlist}

  \begin{cvlist}{Conference Organization}

  \item[] Organizer of Session at the Canadian Society of Chemistry Conference 2026, \textbf{Title}: Crystal Structure Prediction and Engineering: From Conventional Tools to AI Approaches (PTC) \textbf{About:} The symposium will explore the full spectrum of crystal structure prediction (CSP) and engineering, from established computational and experimental approaches to emerging AI-driven techniques.
      
   \end{cvlist}

  \begin{cvlist}{Other Skills}
  \item[] Named developer for FHI-aims Software package.
  \item[] FORTRAN programming language.
  \item[] Python programming language.
  \item[] Bash command language. 
  \item[] GNU/Linux OS.
  \item[] Skills working with high-performance computing, and high-throughput computing. 
  \item[] Computer hardware and construction.
  \item[] Computational method development and coding.
  \item[] Wide array of chemical and materials knowledge.
  \item[] MSOffice suite.
  \item[] Github and GitLab.
  \end{cvlist}
  
  \setlength{\cvlabelwidth}{2.0cm}\begin{cvlist}{Awards}
  \item[{\bf 2023-2024}] Dalhousie Openthink Scholar, Dalhousie University, Halifax.
  \item[{\bf 2022}] Douglas E. Ryan Prize for Excellence in Graduate Studies in Chemistry, Dalhousie University, Halifax.
  \item[{\bf 2022}] Chemistry Graduate Student Society -- Student
    Travel Grant --  Dalhousie University, Halifax.
    \item[{\bf 2022}] Canadian Society for Chemistry Conference Student
    Award --  Graduate -- Physical / Theoretical -- awarded for the best graduate-student poster presentation at the 2022 CSTCC. 
    \item[{\bf 2021}] The Gerry Dauphinee Graduate Scholarship in Chemistry, Dalhousie University, Halifax.
    \item[{\bf 2020}] Mitacs Globalink Research Award -- 
    Max Planck Institute for the Structure and Dynamics of Matter, Hamburg, Germany.
    \item[{\bf 2019}] Chemistry Graduate Student Society -- Student
    Travel Grant -- Dalhousie University, Halifax.
    \item[{\bf 2019}] Faculty of Science Undergraduate Research Prize, Dalhousie University, Halifax.
    \item[{\bf 2019}] Hypercube Scholar Award, for the top graduating Honours student in theoretical / computational chemistry, Dalhousie University, Halifax.
    \item[{\bf 2018-2019}] Dean's List, Dalhousie University, Halifax.
    \item[{\bf 2018}] Dalhousie In-course Scholarship, Dalhousie University, Halifax.
    \item[{\bf 2012-2013}] Chemistry, Ozin Group -- Summer Research Student -- The University of Toronto, Toronto.
  \end{cvlist}

\setlength{\cvlabelwidth}{4.0cm} \begin{cvlist}{Teaching}
    \item[{\bf University of Toronto}]

    \item[March 2025] CHM 328H - Modern Physical Chemistry, Guest Lecturer (2 weeks)
    
    \item[{\bf Dalhousie University}]
    %\item[\rule{3mm}{0pt} {\bf Dalhousie University}]
    
     \item[Jan 2019 - May 2023] CHEM 1022 - Engineering Chemistry II, Senior TA (500 students)
    \item[Jan 2019 - May 2023] CHEM 1012 - Concepts in Chemistry: Energy and Equilibrium, Senior TA (500 students)
    \item[Sept 2018 - May 2023] CHEM 1021 - Engineering Chemistry I, Senior TA (500 students)
    \item[Sept 2018 - May 2023] CHEM 1011 - Concepts in Chemistry: Structure and Reactivity, Senior TA (500 students)

     \item[Jan 2018 - May 2018] CHEM 1022 - Engineering Chemistry II, Course TA (500 students)
    \item[Jan 2018 - May 2018] CHEM 1012 - Concepts in Chemistry: Energy and Equilibrium, Course TA (500 students)
    \item[Sept 2017 - Dec 2017] CHEM 1021 - Engineering Chemistry I, Course TA (500 students)
    \item[Sept 2017 - Dec 2017] CHEM 1011 - Concepts in Chemistry: Structure and Reactivity, Course TA (500 students)
    
  \end{cvlist}
    
\setlength{\cvlabelwidth}{0.5cm}
  \begin{cvlist}{Professional Affiliations}
    \item[] American Chemical Society (ACS)
    \item[] Canadian Society for Chemistry (CSC)
    \item[] World Association of Theoretical and Computational
    Chemists (WATOC)
  \end{cvlist}

  

%   \begin{cvlist}{Lab Experience}
%     \item[] 2011-2012 Laboratory Research under Dr.\ Duncan Wild using a Time-Of-Flight Photoelectron Spectrometer
%     \item[] 2010 Water Corporation - Subiaco Waste Water Treatment Plant
%     \item[] 2009-2012 Conducting Laboratory Demonstrations and classes
%     at all levels of University education at the University of Western Australia and the University of California Merced
%     \item[] 2007 Australian National University Laboratories under the supervision of Dr. Mark Ellison
%   \end{cvlist}

%  \begin{cvlist}{Volunteering and Community Outreach}
%    \item[] 2023 Dalhousie OpenThink Initiative cohort member
%    \item[] 2022-2023 Graduate Student Representative for Physical, Theoretical and Computational Chemistry Division of Chemical Institute of Canada
%    \item[] 2022-2023 Chemistry Graduate Student Society, President (Dalhousie University)
%    \item[] 2021-2022 Para-rowing Coordinator and Coach (Argonauts Rowing Club, Toronto)
%    \item[] 2020-2022 Chemistry Graduate Student Society, VP Finance (Dalhousie University)
%    \item[] 2017 Atlantic Theoretical Chemistry Symposium (ACTS2017) Local Organiser
%  \end{cvlist}
%

%  \begin{cvlist}{References}
%    \item[] Prof.\ Erin R.\ Johnson \\
%    Dalhousie University \\
%    Halifax, NS, Canada \\
%    erin.johnson@dal.ca \\
%    +1 902-494-3409
%    \item[] Assoc.\ Prof.\ Jesse Maassen \\
%    Dalhousie University, \\
%    Halifax, NS, Canada \\
%    jmaassen@dal.ca \\
%    +1 902-494-2792
%    \item[] Prof.\ Axel D.\ Becke \\
%    Dalhousie University\\
%    Halifax, NS, Canada \\
%    axel.becke@dal.ca \\
%    +1 902-494-2986

%  \end{cvlist}

\end{cv}


\end{document}










